`dads`: a modular `R` package for simulating diversity and traits data.

### 2023-01-19 inst/dads_paper.Rmd
Update dads_paper.Rmd

# Data Availability, repeatability and reproducibility

The raw empirical data is available from the original papers [@beck2014; @jones2015, @marcy2016; @hopkins2016; @wright2017; @healy2019].
The subsets of the empirical data used in this analysis are available on figshare 
[DOI: 10.6084/m9.figshare.9943181.v1](https://doi.org/10.6084/m9.figshare.9943181.v1).
The modified empirical data are available in the package accompanying this manuscript (`data(moms::demo_data)`).
This manuscript (including the figures, tables and supplementary material) is repeatable and reproducible by compiling the vignette of the [GitHub `moms R` package](https://github/TGuillerme/moms).

>>>>

# Repeatability and reproducibility

No data was used for this paper. However the entire paper (plots and results) is reproducible by compiling the paper in `Rmarkdown` from [github](link_to_the_paper). <!-- TODO: link to the Rmd file -->
